Automated data-driven symbolic modeling of the lift forces acting on flapping wings

### 2021-02-07 paper/main.tex
Add TODO
Capitalize v in v-squared expressions

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
{\bf Contribution} & {\bf Analytical} & {\bf Data-Driven ($EQ_4$)}\\
\hline
Aerodynamic Lift & \(\nicefrac{1}{2}\rho v^2AC_{Lmax}\sin(2\alpha)\) & \(C_2RX_{CM}\psi\dot{\phi}\)\\
Pendulum 1 & \(M\cdot Y_{CM}\ddot{\psi}\sin{\psi}\) & \it{None} \\
Pendulum 2 & \(M\cdot Y_{CM}\dot{\psi}^2\cos{\psi}\) & \(C_1R\cdot Y_{CM}\dot{\psi}^2\cos{\psi}\) \\
Deviation 1 & \(\approx-MX_{CM}\ddot{\theta}\) & \(- C_3R\ddot{\theta}\)\\
Deviation 2 & \(\approx0\) & \it{None} \\
%Deviation 2 & \(X_{CM}M\dot{\theta}^2\sin\theta\) & \(<none>\)\\
\hline
\end{tabular}
\caption{\label{table:eqcorrespondence}Correspondence between analytical and data-driven terms.}
\end{table}

@@

Nevertheless, in some domains such as flapping flight, there exist high degrees
of correlation between certain variables.  For example, the center of area
location in a rectangular wing is closely related to its span and chord length.
Similarly, kinematic variables such as stroke and deflection angles are highly
correlated with each other and their derivatives across all 58 experiments,
making these variables approximately interchangeable with each other when
coefficients are adjusted accordingly.  This behavior provides an explanation
for why \(\psi\dot{\phi}\) is used as an approximation for an aerodynamic lift
term proportional to \(v^2\).  These correlations between variables are
inherent in highly symmetric, periodic phenomena such as flapping flight.  In
principle, additional experiments could be performed on flapping surfaces that
are not bound to the natural kinematics of flapping wings to explore the full
parameter space and disambiguate non-physical terms in the candidate models.

>>>>

% TODO: Make correspondence more explicit. For example, mass M is a direct
% stand-in for wingspan R with a coefficient.

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
{\bf Contribution} & {\bf Analytical} & {\bf Data-Driven ($EQ_4$)}\\
\hline
Aerodynamic Lift & \((\nicefrac{1}{2})\rho V^2AC_{Lmax}\sin(2\alpha)\) & \(C_2RX_{CM}\psi\dot{\phi}\)\\
Pendulum 1 & \(M\cdot Y_{CM}\ddot{\psi}\sin{\psi}\) & \it{None} \\
Pendulum 2 & \(M\cdot Y_{CM}\dot{\psi}^2\cos{\psi}\) & \(C_1R\cdot Y_{CM}\dot{\psi}^2\cos{\psi}\) \\
Deviation 1 & \(\approx-MX_{CM}\ddot{\theta}\) & \(- C_3R\ddot{\theta}\)\\
Deviation 2 & \(\approx0\) & \it{None} \\
%Deviation 2 & \(X_{CM}M\dot{\theta}^2\sin\theta\) & \(<none>\)\\
\hline
\end{tabular}
\caption{\label{table:eqcorrespondence}Correspondence between analytical and data-driven terms.}
\end{table}

@@

Nevertheless, in some domains such as flapping flight, there exist high degrees
of correlation between certain variables.  For example, the center of area
location in a rectangular wing is closely related to its span and chord length.
Similarly, kinematic variables such as stroke and deflection angles are highly
correlated with each other and their derivatives across all 58 experiments,
making these variables approximately interchangeable with each other when
coefficients are adjusted accordingly.  This behavior provides an explanation
for why \(\psi\dot{\phi}\) is used as an approximation for an aerodynamic lift
term proportional to \(V^2\).  These correlations between variables are
inherent in highly symmetric, periodic phenomena such as flapping flight.  In
principle, additional experiments could be performed on flapping surfaces that
are not bound to the natural kinematics of flapping wings to explore the full
parameter space and disambiguate non-physical terms in the candidate models.
